Make manuscript figures

### 2021-10-28 scripts/R/make_manuscript_figures.rmd
fix x-axis labels in GWAS simulation plot

# Plot RMSE
rmse_plot <- plotHeatmap(
        df = data.summary,
        N.sim = data.summary$N.reps[[1]],
        is.MLE = T,
        scale.limits = c(0, 1),
        legend.name = "RMSE",
        midpoint = 0.5,
        fill.hi = RColorBrewer::brewer.pal(name = 'PiYG', n = 3)[1],
        fill.lo = RColorBrewer::brewer.pal(name = 'PiYG', n = 3)[3],
        fill.mid = RColorBrewer::brewer.pal(name = 'PiYG', n = 3)[2],
        x.var = "alpha",
        y.var = "H2",
        fill.var = "mean.error",
        facet.x = "inference.method",
        facet.y = NA,
        is.oob.squish = F,
        is.real.scale = F,
        labeller = label_wrap_gen(width = 25)) +
        labs(x = expression("Selection strength (" * alpha * ")"),
             y = expression("spVL heritability (" * italic('H'^2) * ")")) +
        shared_theme +
        theme(axis.text.x = element_text(angle = 90)) +
        geom_point(data = spvl_data, fill = "black")

@@

# Plot TPR
tpr_plot <- makeTPRPlot(
        df = data.summary %>% filter(inference.method %in% c(e_name, ehat_name, z_minus_zbar_name)),
        is.MLE = T,
        midpoint = 0.5,
        fill.lo = RColorBrewer::brewer.pal(name = 'RdBu', n = 3)[3],
        fill.hi = RColorBrewer::brewer.pal(name = 'RdBu', n = 3)[1],
        fill.mid = RColorBrewer::brewer.pal(name = 'RdBu', n = 3)[2]) +
        facet_grid(. ~ inference.method, labeller = label_wrap_gen(width = 25)) +
        labs(x = expression("Selection strength (" * alpha * ")"),
             y = expression("spVL heritability (" * 'H'^2 * ")")) +
        shared_theme +
        theme(axis.text.x = element_text(angle = 90)) +
        geom_point(data = spvl_data, fill = "black")

>>>>

# Plot RMSE
rmse_plot <- plotHeatmap(
        df = data.summary,
        N.sim = data.summary$N.reps[[1]],
        is.MLE = T,
        scale.limits = c(0, 1),
        legend.name = "RMSE",
        midpoint = 0.5,
        fill.hi = RColorBrewer::brewer.pal(name = 'PiYG', n = 3)[1],
        fill.lo = RColorBrewer::brewer.pal(name = 'PiYG', n = 3)[3],
        fill.mid = RColorBrewer::brewer.pal(name = 'PiYG', n = 3)[2],
        x.var = "alpha",
        y.var = "H2",
        fill.var = "mean.error",
        facet.x = "inference.method",
        facet.y = NA,
        is.oob.squish = F,
        is.real.scale = F,
        labeller = label_wrap_gen(width = 25)) +
        labs(x = expression("Selection strength (" * alpha * ")"),
             y = expression("spVL heritability (" * italic('H'^2) * ")")) +
        shared_theme +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
        geom_point(data = spvl_data, fill = "black")

@@

# Plot TPR
tpr_plot <- makeTPRPlot(
        df = data.summary %>% filter(inference.method %in% c(e_name, ehat_name, z_minus_zbar_name)),
        is.MLE = T,
        midpoint = 0.5,
        fill.lo = RColorBrewer::brewer.pal(name = 'RdBu', n = 3)[3],
        fill.hi = RColorBrewer::brewer.pal(name = 'RdBu', n = 3)[1],
        fill.mid = RColorBrewer::brewer.pal(name = 'RdBu', n = 3)[2]) +
        facet_grid(. ~ inference.method, labeller = label_wrap_gen(width = 25)) +
        labs(x = expression("Selection strength (" * alpha * ")"),
             y = expression("spVL heritability (" * 'H'^2 * ")")) +
        shared_theme +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
        geom_point(data = spvl_data, fill = "black")
